Full-day, in home validation of infant body position measurements from inertial sensors

### 2023-02-11 manuscript.Rmd
data files organized

# Goal 1: Optimize and validate body position classification model

# Goal 2: Assess classification accuracy across a long delay

# Goal 3: Examine wear time and compliance in full-day data collection

# Goal 4: Compare classification estimates to prior literature

>>>>

# Goal 1: Optimize and validate body position classification model
<!--resampled-metrics, splithalf-metrics, predictions CSVs generated from tune_ml/classification_tidymodels.R -->

# Goal 2: Assess classification accuracy over long recordings
<!-- compiled_agreement.csv, generated from analysis-pt2/compile_agreement.R -->

# Goal 3: Compare classification estimates to prior literature
<!-- imu-compiled.csv, generated from analysis-lena-imu/compile_lena_imu.R -->

# Goal 4: Examine wear time and compliance in full-day data collection
<!-- imu-compiled.csv, generated from analysis-lena-imu/compile_lena_imu.R -->
